\textbf{ \Large{Decentralized autonomous sensor fault detection using neural networks}}

### 2015-01-23 Paper/PaperJahrSchlich.tex
Änderungen aus Besprechung

The dependability and the accuracy of structural health monitoring systems can be affected significantly by sensor faults. 
In this paper, the design and implementation of a wireless structural health monitoring system, capable of decentralized autonomous fault detection, are presented. 
For self-detecting sensor faults, each sensor node predicts expected sensor data and compares it to the measured sensor data. 
The predictions are computed using neural networks based on measured sensor data of adjacent sensor nodes.
In laboratory experiments, devised to validate the proposed approach, several simulated sensor faults are detected.
These results indicate that the use of neural networks for fault detection increases the dependability and the accuracy of structural health monitoring systems.

@@

Civil engineering structures are exposed to various external impacts during their lifetime. 
Structural health monitoring (SHM) systems can be deployed to evaluate the conditions and to ensure the structural stability of civil engineering structures.
\cite[4]{BisbySHM} defines SHM as "a non-destructive \textit{in-situ} structural evaluation method that uses any of several sensors which are attached to, or embedded in, a structure".
The obtained sensor data is collected by sensor nodes, and then analyzed and stored on a computer system over long periods of time. 
Analysis of the sensor data can reveal abnormal changes in material and geometric behaviour early on.

Traditionally, the sensor nodes are wired with cables and connected to computer systems.
However, using wired SHM systems has several disadvantages, including expensive wiring, high installation and labor costs and inaccessibility of optimal sensor location with wires.
In wireless SHM systems, the sensor nodes communicate---through a basestation with each other and with computer systems--- via wireless transceivers, eradicating wiring-specific problems.

Over their lifetime, sensors can become inaccurate, faulty, or may even break.
A fault can be defined as a defect of a sensor, that leads to an error. An error is the manifestation of a fault---an incorrect system state---that may result in a failure.
To ensure the dependability and the accuracy of the SHM system, sensor faults must be detected and isolated in real time. 
The traditional approach to fault detection is the installation of physically redundant sensors.
Faulty sensors can easily be identified through the deviation of their measurements from the measurements of correlated sensors.
Physical redundancy, although efficient for sensor fault detection, shows the disadvantage of increased installation and maintenance costs. 
Representing a more efficient approach, analytical redundancy typically uses mathematical functions mapping the characteristics of the structure and the correlations of the installed sensors. Virtual sensor measurements are computed for each sensor and then compared to the actual measurements. 
For example, finite element models can be used in combination with data from adjacent sensor nodes to calculate virtual measurements of a sensor.
\citep{Smarsly2014}

In this study, analytical redundancy is implemented into wireless sensor nodes based on artificial neural networks.
Artificial neural networks essentially consist of interconnected data processing units called neurons. 
Neurons are grouped in different layers; usually one input layer, a number of hidden layers and one output layer.
Artificial neural networks have the distinct ability of learning, which is achieved by adjusting the weights of the inter-neuron connections until a set of given input variables results in the desired output variables; for example, a neural network can be trained to approximate any mathematical functions with arbitrary accuracy \citep{Li2011}.

This paper is organized as follows:
First, a wireless structural health monitoring system is designed and implemented. 
Next, a neural network is implemented into each sensor node and trained to predict the sensor measurements of said node in order to detect sensor faults in a decentralized manner. 
Then, the system is tested in laboratory experiments. 
Finally, the experimental results are discussed and future research directions are proposed.

@@

Tasks 1 to 3 are usually implemented on site, while tasks 4 to 6 are usually implemented on computer systems off site.
A wireless SHM system installed on the building site consists of sensor nodes attached to the construction, a base station, and a local computer. 
The base station, which can be an external device or a computer program, links the individual sensor nodes with each other and the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
In this project, the acceleration is measured using wireless sensor nodes and a basestation of the type "Oracle Sun SPOT". 
The 3-axis digital output accelerometer with sensitivity ranging between $ \pm $ 2G and $\pm$ 8G has a maximum sample rate of 125Hz. \cite[9]{eDemo2010}

>>>>

The dependability and the accuracy of structural health monitoring systems can be affected by sensor faults. 
In this paper, the design and implementation of a wireless structural health monitoring system, capable of decentralized autonomous fault detection, are presented. 
For self-detecting sensor faults, each sensor node predicts expected sensor data and compares it to the measured sensor data. 
The predictions are computed using neural networks based on measured sensor data of adjacent sensor nodes.
In laboratory experiments, devised to validate the proposed approach, several simulated sensor faults are detected.
These results indicate that the use of neural networks for fault detection increases the dependability and the accuracy of structural health monitoring systems.

@@

Civil engineering structures are exposed to various external impacts during their lifetime. 
Structural health monitoring (SHM) systems can be deployed to evaluate the conditions and to ensure the structural stability of civil engineering structures.
\cite[4]{BisbySHM} defines SHM as "a non-destructive \textit{in-situ} structural evaluation method that uses any of several sensors which are attached to, or embedded in, a structure".
The obtained sensor data is collected by sensor nodes, and then analyzed and stored on a computer system over long periods of time. 
The analysis of the sensor data can reveal abnormal changes in material and geometric behaviour early on.

Traditionally, the sensor nodes are connected to computer system with cables.
However, using wired SHM systems has several disadvantages, including expensive wiring, high installation and labor costs as well as inaccessibility of optimal sensor location with wires.
In wireless SHM systems, the sensor nodes communicate---through a basestation with each other and with computer systems--- via wireless transceivers, eradicating wiring-specific problems.

Over their lifetime, sensors can become inaccurate, faulty, or may even break.
A fault can be defined as a defect of a sensor that leads to an error. An error is the manifestation of a fault---an incorrect system state---that may result in a failure.
To ensure the dependability and the accuracy of the SHM system, sensor faults must be detected and isolated in real time. 
The traditional approach to fault detection is the installation of physically redundant sensors.
Faulty sensors can be identified through the deviation of their measurements from the measurements of correlated sensors.
Physical redundancy, although efficient for sensor fault detection, causes increased installation and maintenance costs due to the multiple installation of sensors. 
Representing a more efficient approach, analytical redundancy typically uses mathematical functions mapping the characteristics of the structure and the correlations of the installed sensors. Virtual sensor measurements are computed for each sensor and then compared to the actual measurements. 
For example, finite element models can be used in combination with data from adjacent sensor nodes to calculate virtual measurements of a sensor.
\citep{Smarsly2014}

In this study, analytical redundancy is implemented into wireless sensor nodes based on artificial neural networks.
Artificial neural networks essentially consist of interconnected data processing units called neurons. 
The neurons are grouped in different layers; usually one input layer, a number of hidden layers, and one output layer.
Artificial neural networks are able to learn, which is achieved by adjusting the weights of the inter-neuron connections until a set of given input variables results in the desired output variables; for example, a neural network can be trained to approximate any mathematical functions with arbitrary accuracy \citep{Li2011}.

This paper is organized as follows:
First, a wireless structural health monitoring system is designed and implemented. 
Next, a neural network is implemented into each sensor node and trained to predict the sensor measurements of the specific node in order to detect sensor faults in a decentralized manner. 
Then, the system is tested in laboratory experiments. 
Finally, the experimental results are discussed and future research directions are proposed.

@@

Tasks 1 to 3 are usually implemented on site, while tasks 4 to 6 are usually implemented on computer systems off site.
A wireless SHM system installed on the building site consists of sensor nodes attached to the construction, a base station, and a local computer. 
The base station, which can be an external device or a computer program, links the individual sensor nodes with each other and the local computer.
To each sensor node, several sensors measuring different physical quantities may be connected. 
In this project, the acceleration is measured using wireless sensor nodes and a basestation of the type "Oracle Sun SPOT". 
The 3-axis digital output accelerometer with sensitivity ranging between $ \pm 2\,$g and $\pm 8\,$g has a maximum sample rate of 125Hz. \cite[9]{eDemo2010}
